Modal Abstractions for Virtualizing Memory Addresses

### 2023-02-22 programlogic.tex
+

\subsection{Aliasing/Sharing Physical Pages}
As we see in Figure \fref{fig:}, virtual address mapping is obtained simply in two fold: 1. traversing the page tables to reach the page table entry 2. fetch the physical address and the value it is adressing (Section \ref{fig:physicalpointsto}). This two fold access pattern enabling sharing of pages by virtual memory addresses exhibits logically sound representation against virtual memory operations some of which ((e.g. mapping a new page) we explain in detail in Section \ref{}.

@@

\subsection{Address-Spaces as a Modality}
\subsubsection{Modal Resource Context}
\subsubsection{Interaction: address-space switch as a modal-entailment}

>>>>

\subsection{Aliasing/Sharing Physical Pages}
\label{sec:sharingpages}
As we see in Figure \fref{fig:}, virtual address mapping is obtained simply in two fold: 1. traversing the page tables to reach the page table entry 2. fetch the physical address and the value it is adressing (Section \ref{fig:physicalpointsto}). This two fold access pattern enabling sharing of pages by virtual memory addresses exhibits logically sound representation against virtual memory operations some of which ((e.g. mapping a new page) we explain in detail in Section \ref{}.

@@

\todo[inline,color=green]{ismail, put the fancy Iris figure for this ghost thing and expand the text above}
\subsection{Address-Spaces as a Modality}
\label{sec:aspacemodal}
Abstractions we introduce for virtual address spaces are based on two pillars: 1. a global address space invariant asserting the authorative ownership of the ghost map, , summarizing the existence of the page-table walks, and for each physical page address reached by one of these abstract page-table walks we know that there exists concrete physical page-table accesses, i.e. L4-L1 pointsto  2. a modal definition describing the truth of assertions for the resources inside the address space, $[r]P$ indicating that $P$ holds in the virtual address space rooted at $r$.
\subsubsection{Global Addressspace Invariant}

\subsubsection{Address-Space Modality}
\paragraph{Modal Resource Context}
\paragraph{Interaction: address-space switch as a modal-entailment}
